---
title: "DADA2 analysis of 16S rRNA gene amplicon sequencing reads"
author: "Jianshu Zhao"
date: "`r Sys.Date()`"
output: 
  pdf_document: default
---

<br>

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width = 10)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```


<br>

## Introduction
Implementing DADA2 pipeline for resolving sequence variants from 16S rRNA gene amplicon **_paired-end_** sequencing reads, adopting the tutorial from https://benjjneb.github.io/dada2/tutorial.html and https://benjjneb.github.io/dada2/bigdata_paired.html with minor adjustments.  This report captures all the workflow steps necessary to reproduce the analysis.

<br>

## Load R packages:  
```{r load_packages, echo=FALSE}

# load packages
library(devtools)
devtools::install_github("vmikk/metagMisc")
library(phyloseq); packageVersion("phyloseq")
library(ggplot2) #Package to generate plots
library(vegan) #community ecology package
library(scales) #To modify scale of plot's axis
library(metagMisc) #Package to manipulate phyloseq objects
library(dplyr) #package used for data manipulation 
library(reshape2) #package used for data manipulation 
library(data.table) #package used for data manipulation 
